A More Complete Algebra for File Synchronization

### 2015-11-14 2015/paper.tex
Introducing new 'works' relation; separating axioms from inference rules

\newcommand{\works}{\dot{\mathbf{w}}}

@@

\theoremstyle{definition}
\newtheorem{mydef}{Definition}
\newtheorem{myax}{Axiom}
\newtheorem{mylem}{Lemma}

\crefname{mydef}{definition}{definitions}
\crefname{myax}{axiom}{axioms}
\crefname{mylem}{lemma}{lemmas}

@@

@@

In the following sections $A,B,S$ and $T$ denote sequences of commands.
The first two relations echo the ones defined in \cite{NREC:alg}.

@@

\begin{mydef}
$\works A$ means that $A$ does not break a filesystem.
Unlike the operators (TODO:?) defined above,
$\works$ ties to the same variable in the whole expression.
For example, the intended interpretation of
$\works A$ is $\exists \FS: A\FS\neq\fsbroken$,
and the intended interpretation of
$\works A\wedge\works B$ is $\exists \FS: A\FS\neq\fsbroken \wedge B\FS\neq\fsbroken$.

Clearly $\works A\Leftrightarrow A\nequiv\cbrk$.

TODO: This is temporary. Check in what expression $\works$ appears
to see if it can be simplified.
\end{mydef}

@@

\begin{myax}
$A\equiv B \Rightarrow A\eqext B$
\end{myax}

\begin{myax}
$A\equiv B \Rightarrow S;A;T\equiv S;B;T$
\end{myax}

\begin{myax}
$A\eqext B \Rightarrow S;A;T\eqext S;B;T$
\end{myax}

\begin{myax}
$A\eqext B \Rightarrow (\works A \Rightarrow \works B)$
\end{myax}

\begin{myax}\label{worksextpostfix}
$\works[A;S] \Rightarrow \works A$
\end{myax}

\begin{mylem}\label{worksinputmatch}
If $A$ and $B$ are minimal sequences, $(\works A\wedge \works B)$,
and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
then their input types must match ($X=Z$).
TODO: Is this an axiom?
\end{mylem}

@@

We assume that $A$ and $B$ are returned by an update detector,
and so they are minimal and do not contain assertion commands.
We also assume that $\FS_A$ and $\FS_B$ are not broken and therefore $A\coworks B$.

@@

In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
that commute with every command in $B\setminus A$.
This is equivalent to saying that those commands are selected from $A\setminus B$
whose paths are unrelated to the paths of the commands in $B\setminus A$.
\end{mydef}

Now we prove that $\reca\FS_B\neq\fsbroken$.

\begin{mylem}
Let $A$ and $B$ be two minimal sequences without assertion commands so that $A\coworks B$.
Then their intersection ($\ordered{A\cap B}$) can also be applied to any filesystem
either can be applied to without breaking it.
\end{mylem}

>>>>

\newcommand{\works}[1]{\dot{\mathbf{w}}({#1})}
\newcommand{\worksc}[2]{\dot{\mathbf{w}}({#1}|{#2})}

@@

\newcommand{\infer}[2]{\begin{array}{c}{#1}\\\hline{#2}\end{array}}
\newcommand{\inferr}[3]{\begin{array}{c}{#1}\\{#2}\\\hline{#3}\end{array}}

\theoremstyle{definition}

\newtheorem{mydef}{Definition}
\crefname{mydef}{definition}{definitions}

\newtheorem{myax}{Axiom}
\crefname{myax}{axiom}{axioms}

\newtheorem{mylem}{Lemma}
\crefname{mylem}{lemma}{lemmas}

\newtheorem{myth}{Theorem}
\crefname{myth}{theorem}{theorems}

\newtheorem{myrul}{Rule}
\crefname{myrul}{rule}{rules}

@@

% -----------------------------

@@

In the following sections $A$ and $B$ stand for arbitrary sequences of commands.
The first two relations echo the ones defined in \cite{NREC:alg}.

@@

\begin{mydef}
$\works{A_1,A_2,\ldots,A_n}$ means that 
$A_1,A_2,\ldots,A_n$ work at the same time.
Its intended interpretation is
\[\exists \FS: A_1\FS\neq\fsbroken \wedge \cdots \wedge A_n\FS\neq\fsbroken\]
\end{mydef}

\begin{mydef}
$\worksc{A_1,A_2,\ldots,A_n}{B_1,B_2,\ldots,B_n}$ means that 
$A_1,A_2,\ldots,A_n$ work where $B_1,B_2,\ldots,B_n$ work.
Its intended interpretation is
\begin{align*}
\forall \FS:&\\ 
&B_1\FS\neq\fsbroken \wedge \cdots \wedge B_n\FS\neq\fsbroken\\
&\Rightarrow\\
&A_1\FS\neq\fsbroken \wedge \cdots \wedge A_n\FS\neq\fsbroken
\end{align*}
\end{mydef}

@@

We have the following inference rules, in which $A,B,A_i,B_i,S$ and $T$ stand for all possible sequences of commands:

\begin{myrul}
\[\infer{A\equiv B}{A\eqext B}\]
\end{myrul}

\begin{myrul}
\[\infer{A\equiv B}{S;A;T\equiv S;B;T}\]
\end{myrul}

\begin{myrul}
\[\infer{A\eqext B}{S;A;T\eqext S;B;T}\]
\end{myrul}

\begin{myrul}
\[\infer{A\eqnrw B}{\worksc{A}{B}}\]
\end{myrul}

\begin{myrul}
\[\infer{\works{A_1,\ldots,A_{n-1},A_n}}{\works{A_1,\ldots,A_{n-1}}}\]
\end{myrul}

\begin{myrul}
\[\infer{\worksc{A_1,\ldots,A_{n-1},A_n}{B_1,\ldots,B_n}}{\worksc{A_1,\ldots,A_{n-1}}{B_1,\ldots,B_n}}\]
\end{myrul}

\begin{myrul}{??? - and vice versa}
\[\infer{\works{A}}{A\nequiv\cbrk}\]
\end{myrul}

\begin{myax}\label{worksextpostfix}
$\worksc{A}{A;S}$ where $A$ and $S$ are arbitrary sequences
\end{myax}

\begin{mylem}\label{worksinputmatch}
If $A$ and $B$ are minimal sequences, $\works{A,B}$,
and there are commands on path $p$ in both $A$ ($\cxy(p, V_Y)\in A$) and $B$ ($\czw(p, V_W)\in B$)
then their input types must match ($X=Z$).
TODO: Is this an axiom?
\end{mylem}

@@

We assume that $A$ and $B$ are returned by an update detector,
and so they are simple sequences.
We also assume that $\FS_A$ and $\FS_B$ are not broken and therefore $\works{A,B}$.

@@

In other words, the sequence $\reca$ we apply to $\FS_B$ consists of all commands from $A\setminus B$
that commute with every command in $B\setminus A$.
\end{mydef}

Now we prove that $\reca\FS_B\neq\fsbroken$, and, in general:

\begin{myth}
If $A, B$ are simple, then $\worksc{[B;\reca]}{A,B}$
\end{myth}

This is trivial unless $\works{A,B}$.

\begin{mylem}
Let $A$ and $B$ be two simple sequences so that $\works{A, B}$.
Then their intersection works on any filesystem
either of them works on:
$\worksc{\ordered{A\cap B}}{A}$, and, by symmetry, for $B$.
\end{mylem}
